---
title: "Iterations and List Columns"
author: "Elaine Yanxi Chen"
date: "`r Sys.Date()`"
output: github_document
---

## Packages and settings

First we load the packages necessary to knit this document.

```{r packages and settings, message = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Lists

```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, FALSE, TRUE, TRUE)
```

Let's look at a list.

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000))
)
```

Accessing list items

```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```


## Loops!

Let's write a `for` loop

```{r}
list_norm =
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, 0.4),
    d = rnorm(20, 100, 1)
  )
```


Here's my function.

```{r}
mean_and_sd = function(x) {
   
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```


Let's try to make this work.

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

But this is painfully repetitive. And also hard to save.

Let's do a `for` loop instead.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}

output
```

If we pnly look at `output`, it is just an empty object with 4 spots. 
When we run `output[[1]]`, we see that the mean and sd for the first list has been calculated and put in the right spot. 


## can we map??

we can map!!

```{r}
map(list_norm, mean_and_sd)

```

The exact same output is produced.

so...what about other functions?

```{r}
map(list_norm, median)
```

map variants...

```{r}
map_dbl(list_norm, median)

map_df(list_norm, mean_and_sd)
```

stack the rows up and condense the table, simplify the output and can be easily saved


## list columns

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    norm = list_norm
  )

listcol_df[["norm"]]

output = map(listcol_df[["norm"]], mean_and_sd)
```


can we add list columns, and then what

save the results into a new column by mapping the norm vectors into the `mean_and_sd` function

```{r}
listcol_df %>% 
  mutate(
    m_sd = map(norm, mean_and_sd)
  ) %>% 
  select(-norm)
```


## What about something more realisitic...


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


Let's nest within weather stations...

```{r}
weather_df %>% 
  nest(data = date:tmin)

weather_nest_df = 
 weather_df %>% 
  nest(data = date:tmin)
```

collapse into a single column; `weather_nest_df` is really just a list column

```{r}
weather_nest_df[["data"]]
```


```{r}
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
```

