---
title: "Writing Functions"
author: "Elaine Yanxi Chen"
date: "`r Sys.Date()`"
output: github_document
---

## Packages and settings

First we load the packages necessary to knit this document.

```{r packages and settings, message = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Z-scores!!

Let's compute the z-score version of a list of numbers.

```{r}
x_vec = rnorm(25, mean = 7, sd = 4)

(x_vec - mean(x_vec)) / sd(x_vec)
```

Suppose you want to do this often.

```{r}
z_scores = function(x){
  
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  z
}
```


```{r}
z_scores(x = x_vec)

z_scores(x = 1:10)

z_scores(x = rbinom(1000, 1, 0.6))

z_scores(x = 3)

z_scores(x = "my name is Jeff")
```

the last one is NA because can't calculate standard deviation of one number


## Let's have multiple outputs

Let's just get the mean and sd from the vector input.

```{r}
mean_and_sd = function(x) {
   
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}

mean_and_sd(x = x_vec)
mean_and_sd(x = 1:10)
mean_and_sd(x = rbinom(1000, 1, 0.5))
```


## Let's start with simulations...

```{r}
x_vec = rnorm(n = 25000, mean = 17, sd = 4)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Can I do this using a function...YUP

```{r}
sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {
  
  x_inside_of_function = rnorm(n = n_obs, mean = true_mean, sd = true_sd)

tibble(
  mean = mean(x_inside_of_function),
  sd = sd(x_inside_of_function)
)
}
```

does it work?

```{r}
sim_mean_sd(n_obs = 25, true_mean = 10, true_sd = 5)

```

Variables created inside the functions stay inside the functions. You will not find them in the global environment.

## Fixing bad stuff

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

```


Let's write a function to get reviews.

```{r}
read_page_reviews = function(url) {
  
  dynamite_html = read_html(url)

  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()

  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)

  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
)

  reviews
}
```

Argument = what changes

Let's try with a URL

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=5"

read_page_reviews(url)
```


What good does this do?

```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_url = str_c(base_url, c(1, 2, 3, 4, 5))

dynamite_reviews = 
  bind_rows(
  read_page_reviews(vec_url[1]),
  read_page_reviews(vec_url[2]),
  read_page_reviews(vec_url[3]),
  read_page_reviews(vec_url[4]),
  read_page_reviews(vec_url[5]),
)
```

page 3 doesn't work because someone included a photo in their review

need to try the learning assessment by myself

